Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s07_problempinning.tex
Prettified/Separated the tikz code to match Troy's format

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \begin{tikzpicture}[scale=0.8]
        % \tikzstyle{v}=[draw, circle, minimum size=0.1cm, scale=0.7, font=\footnotesize]
        \tikzstyle{v}=[font=\footnotesize]

        \node[v] (a) at (0,0) {A};
        \node[v] (b) at (0,1) {B};
        \node[v] (c) at (1,0) {C};
        \node[v] (d) at (1,1) {D};
        \node[v] (e) at (0,2) {E};
        \node[v] (f) at (1,2) {F};
        \node[v] (g) at (-1,0) {G};
        \node[v] (h) at (-1,1) {H};

        \draw (a) to [bend right=10](b);
        \draw (a) to [bend left=10](b);
        \draw (a) to [bend right=10](c);
        \draw (a) to [bend left=10](c);
        \draw (d) to [bend right=10](c);
        \draw (d) to [bend left=10](c);
        \draw (b) to [bend right=10](d);
        \draw (b) to [bend left=10](d);
        \draw (b) to [bend right=10](e);
        \draw (b) to [bend left=10](e);
        \draw (b) to [bend right=10](h);
        \draw (b) to [bend left=10](h);
        \draw (g) to [bend right=10](h);
        \draw (g) to [bend left=10](h);
        \draw (g) to [bend right=10](a);
        \draw (g) to [bend left=10](a);
        \draw (f) to [bend right=10](e);
        \draw (f) to [bend left=10](e);
        \draw (f) to [bend right=10](d);
        \draw (f) to [bend left=10](d);
    \end{tikzpicture}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.3\linewidth}\centering\scriptsize
    \begin{tikzpicture}
    [level 1/.style={sibling distance=8em},
     level 3/.style={sibling distance=1em}, level distance=0.75cm]
        \tikzstyle{n}=[draw, fill, circle]

        \node (a) at (0,0) {A,B,C,D,E,F,G,H}
            child { node {A,B,C,D,E,F} 
                child { node {C,D,E,F}
                    child {node { }}
                    child {node {...}}
                    child {node { }}
                    child {node { }}
                    } 
                child { node (shared) {A,B,C,D}
                    child {node {A}}
                    child {node {B}}
                    child {node {C}}
                    child {node {D}}
                    } 
                }
            child { node {A,B,C,D,G,H} 
                child { node { } }
                child { node {{\bf A,B,G,H}} 
                    child {node { }}
                    child {node {...}}
                    child {node { }}
                    child {node { }}
                }
            };

    \end{tikzpicture}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}

>>>>

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.3\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
